Thermodynamic fragments for magic states in quantum computation

### 2021-03-16 magic_paper.tex
Summary of possible comparisons added

>>>>

A recent distillation bound was introduced in~\cite{Seddon2020}, where they show that for the deterministic conversion of $n$ copies of a qubit state $\rho$ to a target pure magic state $\ket{\psi}$, the following bound on the distillation rate holds,
\begin{equation}\label{eq:seddon}
	\frac{n'}{n} \leq \frac{\log{\Lambda^+(\rho)}}{\log{F(\psi)^{-1}}},
\end{equation}
where $\Lambda^+(\rho)$ is the generalised robustness of state $\rho$, calculable via a costly SDP and $F(\psi)$ denotes the stabilizer fidelity of state $\ket{\psi}$.
They demonstrate the performance of their bound by considering the purification process of the qubit magic state $\ket{H}$, with their figure replicated in~\cref{fig:seddon}. 
For high initial noise level ($\epsilon = 0.25$), their bound dictates that $R = 1/150$, which is pretty good.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{figs/seddon.png}
    \caption{\textbf{Comparison of Seddon \textit{et al.}'s bound~\cite{Seddon2020} in~\cref{eq:seddon} with a generic resource bound in~\cite{Fang2020}.}
    The process they consider is purifying $n$ copies of $(1-\epsilon)\ketbra{H} + \epsilon/3 \id$ to $n'$ copies of $(1-\epsilon')\ketbra{H} + \epsilon'/3 \id$.
    Their bound (red and blue) is pretty good compared with the generic (violet) bound.
    Not sure why it looks like their bound gives $n\rightarrow 25$ as $1-\epsilon \rightarrow 1$.
    }
    \label{fig:seddon}
\end{figure}

Similar concrete rates have been studied for qudits in two occasions:
First, the mana bound, which we have demonstrated in~\cref{fig:distill_bounds}.
Secondly, Wang \textit{et al.}'s max-thauma bound~\cite{Wang2020}, which as far as I can tell, is less tight than mana (?).
It is defined via an SDP, but we can use its properties (super-additivity and zero at free states) to readily get a bound on noisy Strange states,
\begin{equation}
	\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \ketbra{\rm{S}} + \epsilon \frac{1}{3}\id = (1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)).
\end{equation}
Their bound simply states that any deterministic single-copy distillation process $\rho^{\otimes n} \longrightarrow \tau$ requires an initial number of copies $n \geq \theta_{\rm{max}}(\rho) / \theta_{\rm{max}}(\tau)$.
Therefore, the rate of our pure Strange state distillation process~\cref{eq:sudist} can only get as tight as
\begin{equation}
	R = 1/n = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon,
\end{equation}
which is less tight than mana as could be readily observed if plotted in~\cref{fig:distill_bounds}.
